Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-10-12 docs/Manuscript.tex
Updated manuscript figures and tables, will update the rest tomorrow

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-09-29}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara,
CA\newline\textsuperscript{2}Department of Economics, University of
Hawaii at Manoa, Honolulu, HI}

@@

Our data contain over 45 million individual AIS messages (\emph{i.e.}
positions) for 371 purse seiners and longliners. A total of 233 vessels
have fished within PIPA waters; 217 did so at least once before 2015.
However, not all vessels continued to fish elsewhere after PIPA
implementation: 34 vessels have no recorded AIS messages after
2015\footnote{The 34 missing vessels might have exited the fishery, been
  decommissioned or sold (therefore changing their AIS and mmsi), or
  turned off their AIS transmitters. In either case, we are not able to
  observe these.}, leaving us with 183 vessels that fished inside PIPA
before its implementation, and continued to fish elsewhere afterward.
New vessels might have also entered the fishery after PIPA closure, and
were likely not exposed to the policy intervention in the pre-treatment
period. To account for this, we identify a subset of vessels which we
track since before the implementation of PIPA, and categorize them as
treated or control vessels. Our treatment and control groups are defined
as follows.

The treatment group contains all vessels (n = 183) that fished within
PIPA at least once before the closure, and that continued to fish
elsewhere afterwards. Vessels in the control group meet all three of the
following conditions: i) vessels never fished within PIPA waters, ii)
vessels belong to other PNA countries, and iii) vessels have fished in
surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
closure. For each vessel meeting these characteristics, we calculate
their total monthly fishing hours. Figure \ref{fig:baci_strict} provides
a visual representation of the vessel-level fishing events that make up
each group through time. Table \ref{tab:baci_n_s} shows the number of
vessels following a BACI design, as well as the fishing hours, before
and after PIPA.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\label{fig:baci_strict}Stream of fishing
events by vessels through time. Each line represents a vessel, with dots
indicating months with fishing activity and colors indicating the pre
and post periods.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
\centering
\begin{tabular}[t]{llrrrr}
\toprule
Gear & Treatment & n & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 85 & 474.47780 & 462.5491 & 0.9748593\\
drifting\_longlines & TRUE & 115 & 544.61935 & 522.8392 & 0.9600085\\
purse\_seines & FALSE & 36 & 59.49026 & 154.5776 & 2.5983673\\
purse\_seines & TRUE & 68 & 52.91534 & 131.5452 & 2.4859561\\
\bottomrule
\end{tabular}
\end{table}

@@

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment. We calculate the monthly
relative distribution of fishing hours by all treated vessels across all
fished EEZs and the high seas. These trends are shown in Figure
\ref{fig:redist_trend_ps}, and the relative temporal change is presented
in Table \ref{tab:ba_disp}. EEZs that had sporadic fishing events were
pooled into a group of ``others'', leaving us with a total of n = 12 and
n = 10\footnote{This number is likely to change upon finalizing the
  spatial analysis of longliners, which is currently running.} spatially
defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'', and PIPA)
for purse seiners and longliners, respectively.

@@

\caption{\label{tab:unnamed-chunk-8}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
\centering
\begin{tabular}[t]{lrr}
\toprule
country & Longliners & Purse seiners\\
\midrule
PIPA & -11.48 & -8.54\\
KIR & 1.28 & 2.76\\
HS & 0.00 & 0.00\\
COK & 0.00 & 0.34\\
FSM & 0.00 & 0.55\\
\addlinespace
MHL & NA & -0.55\\
NRU & 0.00 & 0.16\\
PNG & 0.00 & -10.02\\
SLB & -8.48 & 2.13\\
TKL & NA & 0.19\\
\addlinespace
TUV & 7.23 & 1.47\\
others & 22.55 & 11.51\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\label{fig:unnamed-chunk-9}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

\begin{table}[!htbp] \centering 
  \caption{\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 95.087$^{***}$ & 99.232$^{***}$ & 38.349$^{***}$ & 41.920$^{***}$ \\ 
  & (5.877) & (5.453) & (7.423) & (8.214) \\ 
  & & & & \\ 
 treated & $-$6.575 & $-$5.597 & $-$3.811 & 6.541 \\ 
  & (4.985) & (4.564) & (4.247) & (5.195) \\ 
  & & & & \\ 
 year &  &  & 12,828.900$^{***}$ & 16,665.590$^{***}$ \\ 
  &  &  & (2,451.444) & (3,717.658) \\ 
  & & & & \\ 
 year2 &  &  & $-$3.178$^{***}$ & $-$4.131$^{***}$ \\ 
  &  &  & (0.609) & (0.923) \\ 
  & & & & \\ 
 post:treated & $-$16.457$^{**}$ & $-$16.739$^{***}$ & $-$17.304$^{***}$ & $-$18.709$^{***}$ \\ 
  & (6.856) & (6.460) & (6.254) & (6.787) \\ 
  & & & & \\ 
 Constant & 59.490$^{***}$ & 65.485$^{***}$ & $-$12,946,334.000$^{***}$ & $-$16,807,078.000$^{***}$ \\ 
  & (4.422) & (6.132) & (2,473,372.000) & (3,759,572.000) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 3,867 & 3,867 & 3,867 & 3,481 \\ 
R$^{2}$ & 0.171 & 0.243 & 0.281 & 0.299 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & $-$11.929 & $-$6.968 & $-$15.550 & $-$6.761 \\ 
  & (7.969) & (7.975) & (10.181) & (11.289) \\ 
  & & & & \\ 
 treated & 70.142$^{***}$ & 72.314$^{***}$ & 71.985$^{***}$ & 14.026$^{*}$ \\ 
  & (7.200) & (7.200) & (7.279) & (7.988) \\ 
  & & & & \\ 
 year &  &  & $-$6,673.971$^{*}$ & 21,188.090$^{***}$ \\ 
  &  &  & (3,606.793) & (5,631.642) \\ 
  & & & & \\ 
 year2 &  &  & 1.657$^{*}$ & $-$5.259$^{***}$ \\ 
  &  &  & (0.894) & (1.398) \\ 
  & & & & \\ 
 post:treated & $-$9.851 & $-$12.290 & $-$12.779 & $-$14.850 \\ 
  & (9.294) & (9.262) & (9.334) & (9.563) \\ 
  & & & & \\ 
 Constant & 474.478$^{***}$ & 449.960$^{***}$ & 6,719,355.000$^{*}$ & $-$21,341,371.000$^{***}$ \\ 
  & (6.328) & (9.440) & (3,633,994.000) & (5,644,837.000) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 9,460 & 9,460 & 9,460 & 8,269 \\ 
R$^{2}$ & 0.027 & 0.041 & 0.042 & 0.094 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Recall that to evaluate the redistribution of fishing effort we only
track fishing vessels that belong to the treated group. In this case, we
calculate the proportion of fishing effort allocated every month to each
spatially explicit region outlined by EEZs and the high seas. For purse
seiners, these represent 9 main EEZs, PIPA, the high seas, and a group
of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly
relative fishing hours that each region received by all 183 treated
vessels. The top-left panel shows the change in fishing effort inside
PIPA, including the preemptive fishing and immediate reduction
previously reported \citep{mcdermott_2018}.

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{\label{fig:unnamed-chunk-17}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for longliners. \textbf{This are preliminar results, contingent
on the spatial analysis currently being run}}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & h\_prop \\ 
\hline \\[-1.8ex] 
 post & $-$0.085$^{***}$ (0.018) \\ 
  countryKIR & 0.251$^{***}$ (0.036) \\ 
  countryHS & $-$0.089$^{***}$ (0.018) \\ 
  countryCOK & $-$0.085$^{***}$ (0.018) \\ 
  countryFSM & $-$0.034 (0.021) \\ 
  countryMHL & $-$0.063$^{***}$ (0.019) \\ 
  countryNRU & $-$0.039$^{**}$ (0.020) \\ 
  countryPNG & 0.098$^{***}$ (0.034) \\ 
  countrySLB & $-$0.023 (0.026) \\ 
  countryTKL & $-$0.072$^{***}$ (0.018) \\ 
  countryTUV & $-$0.024 (0.021) \\ 
  countryothers & 0.016 (0.021) \\ 
  post:countryKIR & 0.113$^{**}$ (0.045) \\ 
  post:countryHS & 0.085$^{***}$ (0.018) \\ 
  post:countryCOK & 0.089$^{***}$ (0.018) \\ 
  post:countryFSM & 0.091$^{***}$ (0.025) \\ 
  post:countryMHL & 0.080$^{***}$ (0.021) \\ 
  post:countryNRU & 0.087$^{***}$ (0.021) \\ 
  post:countryPNG & $-$0.015 (0.037) \\ 
  post:countrySLB & 0.107$^{***}$ (0.031) \\ 
  post:countryTKL & 0.087$^{***}$ (0.019) \\ 
  post:countryTUV & 0.100$^{***}$ (0.025) \\ 
  post:countryothers & 0.201$^{***}$ (0.028) \\ 
  Constant & 0.089$^{***}$ (0.018) \\ 
 \hline \\[-1.8ex] 
Observations & 864 \\ 
R$^{2}$ & 0.557 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

\section{Appendix}\label{appendix}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:purse_old}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 95.087$^{***}$ & 99.232$^{***}$ & 146.372$^{***}$ & 119.222$^{***}$ \\ 
  & (5.877) & (5.453) & (6.926) & (6.717) \\ 
  & & & & \\ 
 treated & $-$6.575 & $-$5.597 & $-$6.050 & 2.925 \\ 
  & (4.985) & (4.564) & (4.095) & (5.052) \\ 
  & & & & \\ 
 post:treated & $-$16.457$^{**}$ & $-$16.739$^{***}$ & $-$14.748$^{**}$ & $-$16.231$^{**}$ \\ 
  & (6.856) & (6.460) & (6.152) & (6.692) \\ 
  & & & & \\ 
 Constant & 59.490$^{***}$ & 65.485$^{***}$ & 36.643$^{***}$ & 53.138$^{***}$ \\ 
  & (4.422) & (6.132) & (6.462) & (10.394) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 3,867 & 3,867 & 3,867 & 3,481 \\ 
R$^{2}$ & 0.171 & 0.243 & 0.301 & 0.320 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & $-$11.929 & $-$6.968 & 8.201 & 17.751$^{*}$ \\ 
  & (7.969) & (7.975) & (11.119) & (10.388) \\ 
  & & & & \\ 
 treated & 70.142$^{***}$ & 72.314$^{***}$ & 72.243$^{***}$ & 13.875$^{*}$ \\ 
  & (7.200) & (7.200) & (7.283) & (7.992) \\ 
  & & & & \\ 
 post:treated & $-$9.851 & $-$12.290 & $-$13.287 & $-$14.750 \\ 
  & (9.294) & (9.262) & (9.344) & (9.569) \\ 
  & & & & \\ 
 Constant & 474.478$^{***}$ & 449.960$^{***}$ & 449.666$^{***}$ & 429.919$^{***}$ \\ 
  & (6.328) & (9.440) & (11.122) & (27.606) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 9,460 & 9,460 & 9,460 & 8,269 \\ 
R$^{2}$ & 0.027 & 0.041 & 0.042 & 0.094 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-10-11}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara,
CA\newline \textsuperscript{2}Department of Economics, University of
Hawaii at Manoa, Honolulu, HI}

@@

Our data contain over 45 million individual AIS messages (\emph{i.e.}
positions) for 371 purse seiners and longliners. A total of 233 vessels
have fished within PIPA waters; 217 did so at least once before 2015.
However, not all vessels continued to fish elsewhere after PIPA
implementation: 34 vessels have no recorded AIS messages after
2015\footnote{The 34 missing vessels might have exited the fishery, been
  decommissioned or sold (therefore changing their AIS and mmsi), or
  turned off their AIS transmitters. In either case, we are not able to
  observe these.}, leaving us with 176 vessels that fished inside PIPA
before its implementation, and continued to fish elsewhere afterward.
New vessels might have also entered the fishery after PIPA closure, and
were likely not exposed to the policy intervention in the pre-treatment
period. To account for this, we identify a subset of vessels which we
track since before the implementation of PIPA, and categorize them as
treated or control vessels. Our treatment and control groups are defined
as follows.

The treatment group contains all vessels (n = 176) that fished within
PIPA at least once before the closure, and that continued to fish
elsewhere afterwards. Vessels in the control group meet all three of the
following conditions: i) vessels never fished within PIPA waters, ii)
vessels belong to other PNA countries, and iii) vessels have fished in
surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
closure. For each vessel meeting these characteristics, we calculate
their total monthly fishing hours. Figure \ref{fig:baci_strict} provides
a visual representation of the vessel-level fishing events that make up
each group through time. Table \ref{tab:baci_n_s} shows the number of
vessels following a BACI design, as well as the fishing hours, before
and after PIPA.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
\caption{\label{fig:unnamed-chunk-20}\label{fig:baci_strict}Stream of
fishing events by vessels through time. Each line represents a vessel,
with dots indicating months with fishing activity and colors indicating
the pre and post periods.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-21}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
\centering
\begin{tabular}[t]{llrrrr}
\toprule
Gear & Treatment & n & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 77 & 39.03181 & 37.79044 & 0.9681958\\
drifting\_longlines & TRUE & 115 & 41.62659 & 40.43857 & 0.9714600\\
purse\_seines & FALSE & 26 & 11.73804 & 20.13247 & 1.7151474\\
purse\_seines & TRUE & 61 & 10.66939 & 18.36289 & 1.7210820\\
\bottomrule
\end{tabular}
\end{table}

@@

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment. We calculate the monthly
relative distribution of fishing hours by all treated vessels across all
fished EEZs and the high seas. These trends are shown in Figure
\ref{fig:redist_trend_ps}, and the relative temporal change is presented
in Table \ref{tab:ba_disp}. EEZs that had sporadic fishing events were
pooled into a group of ``others'', leaving us with a total of n = 23 and
n = 0\footnote{This number is likely to change upon finalizing the
  spatial analysis of longliners, which is currently running.} spatially
defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'', and PIPA)
for purse seiners and longliners, respectively.

@@

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{\label{fig:unnamed-chunk-25}\label{fig:all_vessels}Fishing hours
and number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

Recall that to evaluate the redistribution of fishing effort we only
track fishing vessels that belong to the treated group. In this case, we
calculate the proportion of fishing effort allocated every month to each
spatially explicit region outlined by EEZs and the high seas. For purse
seiners, these represent 9 main EEZs, PIPA, the high seas, and a group
of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly
relative fishing hours that each region received by all 176 treated
vessels. The top-left panel shows the change in fishing effort inside
PIPA, including the preemptive fishing and immediate reduction
previously reported \citep{mcdermott_2018}.

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-29-1.pdf}
\caption{\label{fig:unnamed-chunk-29}\label{fig:redist_trend_ps}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
\caption{\label{fig:unnamed-chunk-31}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & h\_prop \\ 
\hline \\[-1.8ex] 
 post & 0.005$^{***}$ (0.001) \\ 
  countryEEZ FSM 1 & 0.052$^{***}$ (0.001) \\ 
  countryEEZ KIR 1 & 0.067$^{***}$ (0.002) \\ 
  countryEEZ KIR 2 & 0.020$^{***}$ (0.001) \\ 
  countryEEZ KIR 3 & 0.250$^{***}$ (0.003) \\ 
  countryEEZ MHL 1 & 0.022$^{***}$ (0.001) \\ 
  countryEEZ NRU 1 & 0.049$^{***}$ (0.001) \\ 
  countryEEZ PNG 2 & 0.184$^{***}$ (0.004) \\ 
  countryEEZ SLB 1 & 0.062$^{***}$ (0.002) \\ 
  countryEEZ TUV 1 & 0.059$^{***}$ (0.001) \\ 
  countryHS & 0.073$^{***}$ (0.001) \\ 
  countryHS COK 1 & 0.001$^{***}$ (0.0004) \\ 
  countryHS FSM 1 & $-$0.004$^{***}$ (0.0003) \\ 
  countryHS KIR 1 & 0.015$^{***}$ (0.001) \\ 
  countryHS KIR 2 & $-$0.001$^{*}$ (0.0003) \\ 
  countryHS KIR 3 & 0.002$^{***}$ (0.0004) \\ 
  countryHS MHL 1 & $-$0.004$^{***}$ (0.0003) \\ 
  countryHS MUS 1 & $-$0.004$^{***}$ (0.0003) \\ 
  countryHS NRU 1 & $-$0.003$^{***}$ (0.001) \\ 
  countryHS PNG 2 & $-$0.001$^{*}$ (0.001) \\ 
  countryHS SLB 1 & $-$0.003$^{***}$ (0.0003) \\ 
  countryHS TUV 1 & $-$0.003$^{***}$ (0.0003) \\ 
  countryPIPA PIPA 1 & 0.083$^{***}$ (0.002) \\ 
  post:countryEEZ FSM 1 & 0.003 (0.002) \\ 
  post:countryEEZ KIR 1 & $-$0.007$^{***}$ (0.002) \\ 
  post:countryEEZ KIR 2 & 0.040$^{***}$ (0.003) \\ 
  post:countryEEZ KIR 3 & $-$0.033$^{***}$ (0.005) \\ 
  post:countryEEZ MHL 1 & $-$0.010$^{***}$ (0.002) \\ 
  post:countryEEZ NRU 1 & $-$0.005$^{***}$ (0.002) \\ 
  post:countryEEZ PNG 2 & $-$0.096$^{***}$ (0.004) \\ 
  post:countryEEZ SLB 1 & 0.026$^{***}$ (0.004) \\ 
  post:countryEEZ TUV 1 & 0.007$^{***}$ (0.002) \\ 
  post:countryHS & 0.034$^{***}$ (0.002) \\ 
  post:countryHS COK 1 & $-$0.005$^{***}$ (0.001) \\ 
  post:countryHS FSM 1 & $-$0.005$^{***}$ (0.001) \\ 
  post:countryHS KIR 1 & 0.024$^{***}$ (0.001) \\ 
  post:countryHS KIR 2 & 0.005$^{***}$ (0.001) \\ 
  post:countryHS KIR 3 & 0.020$^{***}$ (0.001) \\ 
  post:countryHS MHL 1 & $-$0.004$^{***}$ (0.001) \\ 
  post:countryHS MUS 1 & $-$0.005$^{***}$ (0.001) \\ 
  post:countryHS NRU 1 & $-$0.006$^{***}$ (0.001) \\ 
  post:countryHS PNG 2 & $-$0.007$^{***}$ (0.001) \\ 
  post:countryHS SLB 1 & $-$0.006$^{***}$ (0.001) \\ 
  post:countryHS TUV 1 & $-$0.005$^{***}$ (0.001) \\ 
  post:countryPIPA PIPA 1 & $-$0.088$^{***}$ (0.002) \\ 
  Constant & 0.004$^{***}$ (0.0003) \\ 
 \hline \\[-1.8ex] 
Observations & 69,048 \\ 
R$^{2}$ & 0.370 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\hypertarget{other-model-specifications}{%
\subsection{Other model
specifications}\label{other-model-specifications}}

\hypertarget{year-as-dummy-variables}{%
\subsubsection{Year as dummy variables}\label{year-as-dummy-variables}}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:purse_old}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 8.394$^{***}$ & 9.334$^{***}$ & 14.934$^{***}$ & 17.284$^{***}$ \\ 
  & (0.267) & (0.254) & (0.312) & (0.403) \\ 
  & & & & \\ 
 treated & $-$1.069$^{***}$ & $-$0.770$^{***}$ & $-$0.993$^{***}$ & 0.259 \\ 
  & (0.249) & (0.234) & (0.219) & (0.269) \\ 
  & & & & \\ 
 post:treated & $-$0.701$^{**}$ & $-$0.899$^{***}$ & $-$0.530$^{*}$ & $-$0.580$^{**}$ \\ 
  & (0.308) & (0.295) & (0.283) & (0.292) \\ 
  & & & & \\ 
 Constant & 11.738$^{***}$ & 11.281$^{***}$ & 7.574$^{***}$ & 10.077$^{***}$ \\ 
  & (0.220) & (0.292) & (0.318) & (0.422) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 37,840 & 37,840 & 37,840 & 37,840 \\ 
R$^{2}$ & 0.087 & 0.136 & 0.179 & 0.192 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:long}Fishing hours from GFW for longliners (n = 203; 88 control, 115 treatment).. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & $-$1.241$^{***}$ & $-$1.026$^{***}$ & $-$0.944$^{***}$ & 13.292$^{***}$ \\ 
  & (0.116) & (0.116) & (0.157) & (0.330) \\ 
  & & & & \\ 
 treated & 2.595$^{***}$ & 2.708$^{***}$ & 2.639$^{***}$ & 1.493$^{***}$ \\ 
  & (0.101) & (0.101) & (0.102) & (0.116) \\ 
  & & & & \\ 
 post:treated & 0.053 & $-$0.069 & $-$0.029 & $-$0.060 \\ 
  & (0.133) & (0.133) & (0.134) & (0.135) \\ 
  & & & & \\ 
 Constant & 39.032$^{***}$ & 38.105$^{***}$ & 38.388$^{***}$ & 36.993$^{***}$ \\ 
  & (0.089) & (0.131) & (0.150) & (0.178) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 227,873 & 227,873 & 227,873 & 227,873 \\ 
R$^{2}$ & 0.010 & 0.015 & 0.016 & 0.030 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
